\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-02-05 5-conclusion.Rmd
chnage the affiliation of nicolas and add CSIRO as Ackno

>>>>

# Acknowledgement

This work is funded by the Commonwealth Scientific and Industrial Research Organisation (CSIRO) Data61 Scholarship and started while Nicolas Langrené was affiliated with CSIRO's Data61. The article is created using `knitr` [@knitr] and `rmarkdown` [@rmarkdown] in R. The source code for reproducing this paper can be found [here](https://github.com/huizezhang-sherry/paper-cubble).

### 2022-02-05 main.Rmd
chnage the affiliation of nicolas and add CSIRO as Ackno

---
documentclass: jss
author:
  - name: H. Sherry Zhang
    # department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    #location: Melbourne, Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  dicook@monash.edu
  - name: Ursula Laa
    # department: Institute of Statistics
    affiliation: 'University of Natural Resources and Life Sciences \AND'
    # location: Vienna, Austria
    # email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    # department: 34 Village Street, Docklands VIC 3008 Australia
    affiliation: 'CSIRO Data61 \AND'
    # location: Melbourne, Australia
    # email: nicolas.langrene@csiro.au
  - name: Patricia Menéndez
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An R Package for Structuring Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Structuring Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  Sptio-temporal data naturally has two levels of observations: site and time level. [problem]. In this paper, a new data structure, `cubble`, is proposed for manipulating and visualising spatio-temporal data.
keywords:
  # at least one keyword must be supplied
  formatted: [spatio-temporal data,  "\\proglang{R}", climate data]
  plain:     [spatio-temporal data, R, climate data]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
  \usepackage{xcolor}
output: rticles::jss_article
bibliography: references.bib
---

>>>>

---
documentclass: jss
author:
  - name: H. Sherry Zhang
    # department: Department of Econometrics and Business Statistics
    affiliation: Monash University
    #location: Melbourne, Australia
    email: \email{huize.zhang@monash.edu}
  - name: Dianne Cook
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  dicook@monash.edu
  - name: Ursula Laa
    # department: Institute of Statistics
    affiliation: 'University of Natural Resources and Life Sciences \AND'
    # location: Vienna, Austria
    # email:  ursula.laa@boku.ac.at
  - name: Nicolas Langrené
    # department: 34 Village Street, Docklands VIC 3008 Australia
    affiliation: 'BNU-HKBU United International College \AND'
    # location: Melbourne, Australia
    # email: nicolas.langrene@csiro.au
  - name: Patricia Menéndez
    # department: Department of Econometrics and Business Statistics
    affiliation: 'Monash University \AND'
    # location: Melbourne, Australia
    # email:  patricia.menendez@monash.edu
title:
  formatted: "\\pkg{cubble}: An R Package for Structuring Spatio-temporal Data"
  # If you use tex in the formatted title, alsoge supply version without
  plain:     "cubble: An R Package for Structuring Spatio-temporal Data"
  # For running headers, if needed
  # short:     "\\pkg{foo}: A Capitalized Title"
abstract: >
  Sptio-temporal data naturally has two levels of observations: site and time level. [problem]. In this paper, a new data structure, `cubble`, is proposed for manipulating and visualising spatio-temporal data.
keywords:
  # at least one keyword must be supplied
  formatted: [spatio-temporal data,  "\\proglang{R}", climate data]
  plain:     [spatio-temporal data, R, climate data]
preamble: >
  \usepackage{amsmath}
  \usepackage{array}
  \usepackage{xcolor}
output: rticles::jss_article
bibliography: references.bib
---

### 2022-02-05 main.tex
chnage the affiliation of nicolas and add CSIRO as Ackno

\author{
H. Sherry Zhang\\Monash University \And Dianne Cook\\Monash University
\AND Ursula Laa\\University of Natural Resources and Life Sciences
\AND Nicolas Langrené\\CSIRO Data61 \AND Patricia
Menéndez\\Monash University \AND
}
\title{\pkg{cubble}: An R Package for Structuring Spatio-temporal Data}

@@

>>>>

\author{
H. Sherry Zhang\\Monash University \And Dianne Cook\\Monash University
\AND Ursula Laa\\University of Natural Resources and Life Sciences
\AND Nicolas Langrené\\BNU-HKBU United International College
\AND Patricia Menéndez\\Monash University \AND
}
\title{\pkg{cubble}: An R Package for Structuring Spatio-temporal Data}

@@

\hypertarget{acknowledgement}{%
\section{Acknowledgement}\label{acknowledgement}}

This work is funded by the Commonwealth Scientific and Industrial
Research Organisation (CSIRO) Data61 Scholarship and started while
Nicolas Langrené was affiliated with CSIRO's Data61. The article is
created using \texttt{knitr} and \texttt{rmarkdown} in R. The source
code for reproducing this paper can be found
\href{https://github.com/huizezhang-sherry/paper-cubble}{here}.
